---
output: pdf_document
urlcolor: blue
---
# Understanding & Quantifying How Paintings are "Valued"
\vspace{-0.4cm}
\begin{center}
\emph{Jessie Bierschenk}
\end{center}
\vspace{-0.6cm}

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.align = 'center', out.extra = '', message = FALSE, warning= FALSE)
```

```{r library, include=FALSE, message=FALSE, warning=FALSE,}
library(tidyverse)
library(readxl)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
#install.packages("knitr")
library(knitr)
library(MASS)
#install.packages("stargazer")
library(stargazer)
#install.packages("ggfortify")
library(ggfortify)
library(kableExtra)
#install.packages("tidyverse")
#install.packages("formattable")
library(formattable)
library("broom")
library(scales)
#install.packages("scales")
library(stargazer)
```

```{r}
data = read_excel("Database_Radermecker.xlsx")
data$HAM_USD = as.numeric(data$HAM_USD)

```


# Introduction

The analyzation of paintings has appeared across various conversations in art, politics, history, and economics, but a question still exists: How do we put a price (as a proxy for value) on such a personal and arbitrary good? Business professionals might say that [appraisals are based largely on what the art has already sold for or typically sells](https://www.artbusiness.com/appsellart.html#:~:text=A%20realistic%20appraised%20value%20is%20based%20largely%20on%20what%20the,that%20have%20already%20taken%20place.); art historians might say that [value is determined by its cultural significance within a given time period.](https://arthistoryproject.com/essays/the-value-of-art/) Yet the question still remains of what objective qualities inherent to a work add value? In the hopes of further exploring such question, this analysis focuses on art auction sales and, by using anonymous works, attempts to strip paintings of their intangible ties to fame or reputation in order to isolate and identify the objective qualities that are associated with art prices. 

[Previous research](https://ideas.repec.org/p/sol/wpaper/2013-264567.html) has identified evidence of a strong assocation between formal naming conventions used by art historians and final auction prices (known as hammer prices). Today, artists are easily identifiable as it has become common practice to sign artwork. In the past (1350-1850), close attention was typically paid to the provisional name of the creator and its long-term recognition, typology, etc. Art markets are characterized by strong asymmetry of information and high uncertainty surrounding quality, leading to difficulty in accurate pricing and therefore emphasizing the importance of the reputation of the creator. To circumvent this reliance on reputation, this analysis will focus on sales of anonymous paintings in an adaption of a dataset from [Anne-Sophie Radermecker's work on naming conventions and anonymous art.](https://ideas.repec.org/p/sol/wpaper/2013-264567.html) The analysis aims to present findings that are easily interpretable for players in the art markets not familiar with highly complex statistical method. The primary research question is as follows:

**(1) What objective, indesputable qualities of a painting are associated with it's value (price) when the connection to its creator is not applicable or controlled for?**

The dataset in this analysis includes 13,211 observations of individual painting sales of 15th-17th century Flemish work and captures sales occuring as early as 1946 to as late as 2015. The data include extensive information for each piece including the naming convention, the working title, the hammer price in 2015 U.S. dollar amount, information about the medium and content of the piece, and information about the date, place, and type of the auction sale. Rademecker describes the full dataset being [mainly collected from the Hislop Art’s Sales Index, and have been systematically compared with data recorded by Artprice and the World Collectors Annuary to provide a comprehensive corpus of sources.](https://ideas.repec.org/p/sol/wpaper/2013-264567.html) 

The dataset includes 1,581 sales of purely anonymous paintings and 11,630 sales of paintings with either a distinct author or some attribution that is expert-verified. [Previous research](https://www.researchgate.net/publication/320007117_An_artist's_perceived_value_Development_of_a_measurement_scale) suggests that "the artist’s name as a brand influences the general assessment of a work and, its economic value and what an art collector is willing to pay for it." Therefore, as mentioned in [Rademecker's research](https://ideas.repec.org/p/sol/wpaper/2013-264567.html), market players wanting to resolve the issue of anonymity in art employ naming strategies developed by art historians to give alternative names to unrecorded artist (attributions). Listed below are conventional naming mechanisms widely used and accepted in contemporary art markets:

* "By" or "By and studio" are used in conjunction with a name when there are records, material, and formal and stylistic evidence of a piece's creator. This is the most specific level of identification and the most "profitable".

* "After" is considered to be a replication of a known artist's work.

* "Attributed to", "Studio of",  and "Circle of" are the next most specific attributes used to indirectly link an anonymous painting to a known artist, style, or school through a verifiable method.

* "Manner of", "School of", "Style of", and "Follower of" are all thought to be the least specific verified attributions types before simply deemed "anonymous".

The more specific the attribution, the more valuable a piece is to a buyer. Art that cannot be given some sort of attribute is considered anonymous. According to Rademecker, there is little work done in art history or economic research that explores this relationship of attributes with price. And, given the guarded and secretive nature art markets, it is difficult to access auction/price data and even more difficult to access information on anonymous, obscure paintings not tied to any creator (attribute);  because of this, this analysis will use the unique opportunity to analyze anonymous work (as well as attribuyted work) to form a more comprehensive understanding of art valuations. The main response vairable of interest in this analysis is the median hammer price (To allow for inflation, prices are deflated using the US Consumer Price Index, and expressed in 2015 US dollars). The median is the intended interest because [meticulous rounding up by auctioneers and theatrical tactics](https://www.taipeitimes.com/News/editorials/archives/2015/11/04/2003631633) can create highly skewed hammer prices; thus, the median is thought to be a more reflective summary statistic.

Table 1 shows the frequency of attribute types in our data set. 12% of the pieces in this dataset are considered anonymous while the rest have some attribute.


```{r}
addparentheses <- function(x){paste("(  ", x, " )")}
data$PI_ATTRIB[data$PI_NAME=="ANONYMOUS_MASTERS"]<-"Anonymous"
data$PI_ATTRIB[data$PI_ATTRIB=="by & studio"]<-"by"

anon_total = length(which(data$PI_ATTRIB == "Anonymous"))
after_total = length(which(data$PI_ATTRIB == "after"))
attrib_total = length(which(data$PI_ATTRIB == "attributed to"))
by_total = length(which(data$PI_ATTRIB == "by"))
circle_total = length(which(data$PI_ATTRIB == "circle of"))
follower_total = length(which(data$PI_ATTRIB == "follower of"))
school_total = length(which(data$PI_ATTRIB == "school of"))
studio_total = length(which(data$PI_ATTRIB == "studio of"))
style_total = length(which(data$PI_ATTRIB == "style of"))
total_attrib = length(data$PI_ATTRIB)

anon_total_per = length(which(data$PI_ATTRIB == "Anonymous"))/length(data$PI_ATTRIB)
after_total_per = length(which(data$PI_ATTRIB == "after"))/length(data$PI_ATTRIB)
attrib_total_per = length(which(data$PI_ATTRIB == "attributed to"))/length(data$PI_ATTRIB)
by_total_per = length(which(data$PI_ATTRIB == "by"))/length(data$PI_ATTRIB)
circle_total_per = length(which(data$PI_ATTRIB == "circle of"))/length(data$PI_ATTRIB)
follower_total_per = length(which(data$PI_ATTRIB == "follower of"))/length(data$PI_ATTRIB)
school_total_per = length(which(data$PI_ATTRIB == "school of"))/length(data$PI_ATTRIB)
studio_total_per = length(which(data$PI_ATTRIB == "studio of"))/length(data$PI_ATTRIB)
style_total_per = length(which(data$PI_ATTRIB == "style of"))/length(data$PI_ATTRIB)


tab_freq_attrib = matrix(c(anon_total, after_total, attrib_total, by_total, circle_total, follower_total, school_total, studio_total,style_total,total_attrib, percent(anon_total_per, accuracy = 0.1),  percent(after_total_per, accuracy = 0.1), percent(attrib_total_per, accuracy = 0.1), percent(by_total_per, accuracy = 0.1), percent(circle_total_per, accuracy = 0.1), percent(follower_total_per, accuracy = 0.1), percent(school_total_per, accuracy = 0.1), percent(studio_total_per, accuracy = 0.1),percent(style_total_per, accuracy = 0.1), "100%"), ncol=10, byrow = TRUE)
colnames(tab_freq_attrib)= c( "Anonymous", "After", "Attributed to", "By", "Circle of", "Follower of", "School of", "Studio of", "Style of", "Total")
rownames(tab_freq_attrib)=c("Count", "Percent")

```

```{r}
tab_freq_attrib %>% 
  kbl(align = rep("c", 4), caption = "Frequency of Attributes in Data") %>%
  kable_styling(latex_options= c("striped","scale_down"))
```


## Exploratory Data Analysis

```{r}

data$Sales_type[data$Sales_type=="Day_sale"] <- "day_sale"
data$PI_TOPIC = factor(data$PI_TOPIC, levels = c("religious", "portrait", "landscape", "allegory", "genre scene", "mythology", "still life", "others"))

data=data %>% 
  mutate(Prev_Attrib = as.factor(ifelse(Prev_attr != "n. m.", 1, 0)), Scientific_Investig = as.factor(ifelse(Sc_investig != 0, 1, 0)), Literature = as.factor(ifelse(Detailed_lit != "n. m.", 1, 0)), Log_Hammer = log(HAM_USD), adj_century = ifelse(is.na(adj_century)==TRUE & school != "n. m.", "16th-17th", adj_century ) )

data$adj_century[data$adj_century==1] <- "15th"
data$adj_century[data$adj_century==2] <- "15th-16th"
data$adj_century[data$adj_century==3] <- "16th"
data$adj_century[is.na(data$adj_century)==T] <- "Missing"
data$CURR[data$CURR=="iTL"] <- "ITL"


data$CURR = as.factor(data$CURR)
data$TYPE_COLLECTION = as.factor(data$TYPE_COLLECTION)
data$DAT = as.factor(data$DAT)
data$PI_MAT = as.factor(data$PI_MAT)
data$PI_ATTRIB = as.factor(data$PI_ATTRIB)
data$SIG = as.factor(data$SIG)

data$CURR <- relevel(data$CURR, ref = "GBP")
data$TYPE_COLLECTION <- relevel(data$TYPE_COLLECTION, ref = "not_mentioned")
data$PI_MAT <- relevel(data$PI_MAT, ref = "panel")
data$PI_ATTRIB <- relevel(data$PI_ATTRIB, ref = "by")

anon_data = subset(data, PI_NAME == "ANONYMOUS_MASTERS")
non_anon_data = subset(data, PI_NAME != "ANONYMOUS_MASTERS")


```

Our response variable of interest is the median hammer price in 2015 US dollars. As shown in **Figure 1**, both anonymous and non-anonymous paintings had a relatively similar shape of price distributions with significant right skew. For non-anonymous paintings, the minimum hammer price in 2015 US dollar equivalent was \$105 and the maximum was \$10,423,009; the median hammer price was \$10,589. For anonymous paintings, the minimum hammer price in 2015 US dollar equivalent was \$263 (higher than non-anonymous) and the maximum was \$2,200,000 (significantly lower than non-anonymous); the median hammer price was \$9,420 ( >\$1,000 less than non-anonymous). This general trend is as expected as the price of anonymous art is not driven up by any particular artist/attribution the way that non-anonymous art is. For both categories, most hammer prices lie in the \$10k - \$50k range.

**Figure 1** shows the log-transformations of the hammer price distribution. Because these distribution are orginally right skewed, a log transformation can reduce skewness in the response and the response more closely reflects a normal distribution shape.

```{r}
hammer_price_non = ggplot(data = non_anon_data, aes(x=HAM_USD))+geom_histogram(fill="blue")+xlim(0,1000000)+ylim(0,3000) + labs(title= "Non-Anonymous Paintings", x= "Hammer Price (2015 USD Equivalent)", y = "Count")
hammer_price_anon = ggplot(data = anon_data, aes(x=HAM_USD))+geom_histogram()+xlim(0,1000000)+ylim(0,500) + labs(title= "Anonymous paintings", x= "Hammer Price (2015 USD Equivalent)", y = "Count")

hammer_price_non_log = ggplot(data = non_anon_data, aes(x=log(HAM_USD)))+geom_histogram(fill="blue") + labs(title= "Log Transformed", x= "Log(Hammer Price (2015 USD Equivalent))", y = "Count")
hammer_price_anon_log = ggplot(data = anon_data, aes(x=log(HAM_USD)))+geom_histogram() + labs(title= "Log Transformed", x= "Log(Hammer Price (2015 USD Equivalent))", y = "Count")
```

```{r, fig.height=3.5}
grid.arrange(hammer_price_non, hammer_price_anon,hammer_price_non_log, hammer_price_anon_log, ncol= 2, top = "Figure 1: Comparison of Hammer Price Distribution Between 
Non-Anonymous and Anonymous Paintings (with Log Transformations)")

```

As discussed previously, research has presented evidence of differences in hammer prices based on attribution status. In **Figure 2** log(hammer price) distributions differ by associated attribution for paintings. The log transformed version is shown to more easily visualize distributions. Paintings that are replications or "copies" of original work appear to have the lowest interquartile range. It's interesting to note that even anonymous paintings have a higher interquartile range than paintings known to not be original. The hammer price distribution associated with by has the largest range; this is likely because the direct link to a particular artist is likely also a direct link to the clout of a particular artist which may significantly vary on a case-by-case basis.

```{r fig.height=2.5, fig.width= 6}
data=data %>% 
  mutate(Anonymous = ifelse(PI_NAME == "ANONYMOUS_MASTERS", 1, 0))
data$PI_ATTRIB = ordered(data$PI_ATTRIB, levels=c("by", "follower of", "studio of", "manner of", "attributed to", "style of","circle of","school of", "after", "Anonymous"))
attrib_price = ggplot(data)+ geom_boxplot(aes(y= PI_ATTRIB,x= log(HAM_USD), fill = as.factor(Anonymous)))+ labs(title = "Figure 2: Log(Hammer Price) Distribution by Attribution", x = "Log(Hammer Price)", y = "Attribution Type")

attrib_price + theme(legend.position = "none")
```
For some objective characteristics, there are distinct differences in between non-anonymous and anonymous paintings. As shown in **Figure 1A**, non-anonymous paintings tend to have more diversity in the paintings' subject while most of the anonymous work is concentrated in religious scences. This is, in part, due to the [growing demand for religious and decorative pictures at the time of the 15th -17th century ](https://www.academia.edu/6145072/Painting_for_the_market_Commercialization_of_art_in_Antwerps_Golden_Age) but still an interesting distinction to make. In terms of similarities, nativity scenes were the most common subject for both anonymous and non-anonymous art followed by portraits and haigographic scenes (scenes depicting saints).

**Figure 2A** illustrates how the median hammer price according to the paintings' subject do not have the same ordinal pattern across anonymous and non-anonymous paintings. For example, the subject matter with the lowest relative median hammer price in non-anonymous art is portraits whereas, among anonymous paintings, portraits have one of the highest relative median hammer prices. Thus, subject matter may be associated with hammer price differently depending on whether a piece is anonymous or not.

```{r}
#1A
Subject_Plot = ggplot(data = anon_data, aes(x=PI_TOPIC))+geom_bar() + labs(title= "Anonymous", x= "Subject", y="Count")+theme(axis.text.x = element_text(angle = 90,hjust=0.95,vjust=0.2))

Subject_Plot2 = ggplot(data = non_anon_data, aes(x=PI_TOPIC))+geom_bar(fill= "blue") + labs(title= "Non-Anonymous", x= "Subject", y="Count")+theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))
```


```{r}
#2A
subject_price = group_by(anon_data, PI_TOPIC)
subject_price = mutate(subject_price, Price_Med = median(HAM_USD, na.rm = T))

data_subject_price = distinct(subject_price, PI_TOPIC, Price_Med)

SubjectPrice_Plot_Condensed = ggplot(data = data_subject_price, aes(PI_TOPIC, Price_Med))+geom_bar(stat= "identity") + labs(title= "Anonymous", x= "Subject", y="Median Hammer Price")+theme(axis.text.x = element_text(angle = 90))

subject_price1 = group_by(non_anon_data, PI_TOPIC)
subject_price1 = mutate(subject_price1, Price_Med = median(HAM_USD, na.rm = T))

data_subject_price1 = distinct(subject_price1, PI_TOPIC, Price_Med)

SubjectPrice_Plot_Condensed1 = ggplot(data = data_subject_price1, aes(PI_TOPIC, Price_Med))+geom_bar(stat= "identity", fill= "blue") + labs(title= "Non-Anonymous", x= "Subject", y="Median Hammer Price")+theme(axis.text.x = element_text(angle = 90))
```

**Figure 3A** illustrates how the log(2015 USD equivalent hammer prices) increased with the date of the recorded sale. As these hammer prices are adjusted for inflation using U.S. CPI, this trend suggests a greater demand/willingness to pay for paintings as the art economy continued to evolve and became more and more sophisticated.

An important thing to note is that not all characteristics differ depending on the anonymous status of a piece. Some relationships are consistent across art regardless of attribution. Through this analysis, we ensure that these characteristics are controlled for and included as we begin our modeling process. **Figure 4A** illustrates that despite the anonymous status of pieces, paintings in specified collection types tend to have higher price distributions than paintings with no information of collection type, and sale records indicate that evening sales tend to have higher price distributions than day sales. 

```{r}
Day_Sale_anon = anon_data
Day_Sale_anon$Sales_type[Day_Sale_anon$Sales_type=="day_sale"] <- "Day"
Day_Sale_anon$Sales_type[Day_Sale_anon$Sales_type=="evening_sale"] <- "Evening"

Day_Sale_non_anon = non_anon_data
Day_Sale_non_anon$Sales_type[Day_Sale_non_anon$Sales_type=="day_sale"] <- "Day"
Day_Sale_non_anon$Sales_type[Day_Sale_non_anon$Sales_type=="evening_sale"] <- "Evening"

anon_sal = ggplot(Day_Sale_anon, aes(x=Sales_type, y=log(HAM_USD)))+geom_boxplot() + labs(tile="Anonymous" , x = "Sale Type" , y = "Log(Hammer Price)")
n_anon_sal=ggplot(Day_Sale_non_anon, aes(x=Sales_type, y=log(HAM_USD)))+geom_boxplot(fill="blue")+labs(tile="Non-Anonymous" , x = "Sale Type" , y = "Log(Hammer Price)")

```

```{r}

Collection_data_a = subset(anon_data, select = c("TYPE_COLLECTION","HAM_USD" ))
Collection_data_a$TYPE_COLLECTION = as.character(Collection_data_a$TYPE_COLLECTION)
Collection_data_a$TYPE_COLLECTION[Collection_data_a$TYPE_COLLECTION=="Belgium_coll"] <- "Belgium"
Collection_data_a$TYPE_COLLECTION[Collection_data_a$TYPE_COLLECTION=="museum_coll"] <- "Museum"
Collection_data_a$TYPE_COLLECTION[Collection_data_a$TYPE_COLLECTION=="noble_coll"] <- "Noble"
Collection_data_a$TYPE_COLLECTION[Collection_data_a$TYPE_COLLECTION=="private_coll"] <- "Private"
Collection_data_a$TYPE_COLLECTION[Collection_data_a$TYPE_COLLECTION== "royal_coll"] <- "Royal"
Collection_data_a$TYPE_COLLECTION[Collection_data_a$TYPE_COLLECTION=="not_mentioned"] <- "No Info"


Collection_data_a$TYPE_COLLECTION = factor(Collection_data_a$TYPE_COLLECTION, levels = c("Belgium", "Museum", "Noble", "Private", "Royal", "No Info"))

Collection_data_na = non_anon_data
Collection_data_na$TYPE_COLLECTION = as.character(Collection_data_na$TYPE_COLLECTION)
Collection_data_na$TYPE_COLLECTION[Collection_data_na$TYPE_COLLECTION=="Belgium_coll"] <- "Belgium"
Collection_data_na$TYPE_COLLECTION[Collection_data_na$TYPE_COLLECTION=="museum_coll"] <- "Museum"
Collection_data_na$TYPE_COLLECTION[Collection_data_na$TYPE_COLLECTION=="noble_coll"] <- "Noble"
Collection_data_na$TYPE_COLLECTION[Collection_data_na$TYPE_COLLECTION=="private_coll"] <- "Private"
Collection_data_na$TYPE_COLLECTION[Collection_data_na$TYPE_COLLECTION=="royal_coll"] <- "Royal"
Collection_data_na$TYPE_COLLECTION[Collection_data_na$TYPE_COLLECTION=="not_mentioned"] <- "No Info"

Collection_data_na$TYPE_COLLECTION = factor(Collection_data_na$TYPE_COLLECTION, levels = c("Belgium", "Museum", "Noble", "Private", "Royal", "No Info"))

collection_anon = ggplot(Collection_data_a, aes(x=TYPE_COLLECTION, y=log(HAM_USD)))+geom_boxplot() + labs(title="Anonymous", x= "Collection Type", y ="Log(Hammer Price)")
collection_non_anon = ggplot(Collection_data_na, aes(x=TYPE_COLLECTION, y=log(HAM_USD)))+geom_boxplot(fill="blue")+ labs(title="Non-Anonymous", x= "Collection Type", y ="Log(Hammer Price)")
```

These findings are all informative for our selection of variables in the model (described in the next section).

# Methodology

In order to distill art valuations to the objective aspects of the art itself, we will create and analyze two models: one model fit to the data only concerning anonymous paintings, and the other fit to the data only concerning paintings with some attribution. These models will (mostly) include the same independent variables.

## (Manipulated) Variables Included

### Shared by Both Models

* The type of sale (day or evening) was included as, traditionally, compared to day sales, evening sales tend to [have fewer works being sold, and these pieces tend to sell at much higher price points](https://www.fineartassetadvisor.com/blog/art-amp-finance-newsletter-35-what-is-the-difference-between-daytime-amp-evening-art-auctions).
* The associated surface area of the piece recorded in the sale is included because this characteristic is a purely objective fact of a work. Because this analysis is interested in objective factors (not tied to the clout or reputation of the creator) that may be associated with the value of art, we will include this. Furthermore, previous [research](https://www.fineartassetadvisor.com/blog/art-amp-finance-newsletter-35-what-is-the-difference-between-daytime-amp-evening-art-auctions) shows evidence of the size of paintings having a positive relationship with price. We divided this variable by 500 and centered it at the mean surface area of the data set (4,956.9 sqr cm) to make for more interpretable results
* The adjunct century of the piece is included as an objective characteristic. This dataset includes 15th - 17th century work with 2,854 missing values for this variable initially. Upon closer examination, all but 3 observations were associated with a school from the 16th-17th century (mentioned in the details of a painting's associated school). With this, an additional category was made to account for 16th - 17th c. work and another category to reflect "missing".
* The associated artistic School which refers to a common [style, inspiration, training, or aims](https://www.thoughtco.com/difference-between-art-styles-schools-and-movements-2573812) was included. This, again, is an objective quality of a piece that may be associated with median hammer price.
* The subject or topic of the piece in a sale and the year of the sale: The subject of a piece is objective and an important distinction to be made when comparing against other pieces. The year of the sale is important in understanding the context of the purchase and the nature of the art economy at the time. Furthermore, as the [taste of art markets change](https://www.royalacademy.org.uk/event/courses-and-classes-a-history-of-the-art-market-an-evolution-of-taste-art-history-theory-business) the prices reflect changes in demand. Therefore, we will also include an interaction term with date purchased and subject to reflect the evolution of preference and trends in the art economy. The date variable was centered at 1946 (the earliest observation in our dataset).
* The currency used in the sale: Currency may indirectly link to the buyer's cultural taste or country of origin. We will include this variable to control for potential preference.
* The collection type associated with the piece sold: Most of the sales do not include this information, but whether a piece was in a private collection (owned by a single entity), or in a museum collection (shown at a museum), etc, is an important factor to control for when understanding price as more well-known pieces may have been showcased more.
* The reputation of the auction house in the sale: This is to control for potential confounding factors driving hammer prices. The status of the auction house is often linked to the quality of works and also buyers.
* A binary variable was created to indicate if there are publications on the painting or not: Having more information or recognition of a piece may be associated with its value.
* A binary variable indicating if the painting was dated or not. Having more information about the exact time period of a piece may be associated with its median hammer price price.
* A variable indicating the material the painting was on and another variable for the medium of the painting (i.e. oil or tempera): These are material and objective characteristics of a piece and are relevant to look at when understanding the value of a piece independent of it's associated authorship status.
* The Consumer Price Index (CPI) is included as it gives context to the state of the (U.S.) economy during the time of the sale. As the U.S. economy is closely intertwined with other developed countries, this proxy is considered adequate for reflecting economic trends during the time of the sale. This variable was centered at the CPI during 1946 (8.3).
* A binary variable indicating if the painting had been in an exhibit or not. Such indication may control for status of a piece and thus what a buyer is willing to bid.


### Unique to Model for Anonymous Paintings

The attribute of "Anonymous" was created to account for pieces in which there was no formal attribution given. This distinction was used when differentiating data that was associated with anonymous and non-anonymous work.
* A binary variable was created to determine if the piece had been reattributed--meaning the original was deemed inaccurate by a relevant expert. For anonymous art, this would mean that the piece had been attributed to an artist or group, and then later determined that such attribution was inaccurate and now it is deemed an "anonymous" work.

### Unique to Model for Non-Anonymous Paintings

For our model fit to non-anonymous data, we will include the attribution type. As mentioned previously, these attributions (naming mechanisms) are important distinctions when considering the valuation of art. For example, a painting that is verified as being "by" a particular artist is more informative for a buyer than "attributed to", "School of", etc., and thus, [the buyer is likely willing to pay more](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2471488). Pieces with the attribute "by & studio" were included in the "by" attribute since both can be associated with a specific artist.
* Indication of the type of reattribution a painting may have had: A painting may have had no reattribution, or a negative reattribution meaning that the piece used to have a more profitable attribution than the one it bears for the sale, or a positive reattribution meaning that the piece used to have a less profitable attribution than the one it bears for the sale. The anonymous paintings do not have positive reattributions because being "anonymous" is regarded as the least profitable attribution.
* Binary indication of whether a painting was examined via scientific technology for authentication purposes: This information further strengthens Only one painting in the anonymous data was associated with this so for the sake of simplicity, it will only be included in the non-anonymous data.
* Binary indication of whether a piece had a signature or not: This allows for greater authentication and information for a buyer, potential associated with median hammer price. Because anonymous works do not have a known author, this variable is unique to the non-anonymous model.

## Removed Variables

With such a large dataset initially with over 500 variables, variables that were redundant or not directly relevant to this analysis were ommitted. See appendix for more explanation.

# Results

For this analysis two models are constructed. One fit to the data of non-anonymous work and the other fit to the data of anonymous work. Both will have the same response variable: ln(Hammer Price 2015 USD Equvalent). Given the skew of the the USD hammer price, this transformation was deemed appropriated to reduce variability.

```{r}
model_a_data = anon_data
model_a_data$Prev_Attrib=as.factor(model_a_data$Prev_Attrib)
model_a_data$EXHIB=as.factor(model_a_data$EXHIB)
model_a_data$t = scale(model_a_data$t)
model_a_data$PI_CPI_OK = (model_a_data$PI_CPI_OK-8.3)
model_a_data$dim2 = (model_a_data$dim2/500)
model_a_data$dim2 = (model_a_data$dim2-(mean(data$dim2)/500))


model_na_data = non_anon_data
model_na_data$EXHIB=as.factor(model_na_data$EXHIB)
model_na_data$TYPE_REATTRIB=as.factor(model_na_data$TYPE_REATTRIB)
model_na_data$t = (model_na_data$t-1946)
model_na_data$TYPE_REATTRIB = relevel(model_na_data$TYPE_REATTRIB, ref = "not_reattributed")
model_na_data$PI_CPI_OK = (model_na_data$PI_CPI_OK-8.3)
model_na_data$dim2 = (model_na_data$dim2/500)
model_na_data$dim2 = (model_na_data$dim2-(mean(data$dim2)/500))

full_model_anon = lm(data= model_a_data, Log_Hammer ~ Sales_type + dim2 + adj_century + BY_SCHOOL + PI_TOPIC + CURR + TYPE_COLLECTION + t + AH_TYPES +PI_TOPIC:t + Literature + DAT + PI_TECH + PI_MAT + PI_CPI_OK + Prev_Attrib + EXHIB)

full_model_non_anon = lm(data= model_na_data, Log_Hammer ~ Sales_type + dim2 + adj_century + BY_SCHOOL + PI_TOPIC + CURR + TYPE_COLLECTION + t + AH_TYPES +PI_TOPIC:t + Literature + DAT + PI_TECH + PI_MAT + PI_CPI_OK + PI_ATTRIB + Scientific_Investig + SIG+ EXHIB + TYPE_REATTRIB)

```


```{r}
final_model_a = tidy(full_model_anon) %>% 
  dplyr::select(-statistic) %>%
  mutate(`Confidence (2.5%)` = exp(as.numeric(estimate) - ((1.96)*as.numeric(std.error))),
         `Confidence (97.5%)` = exp(estimate + ((1.96)*std.error)),
          Significant = ifelse(p.value < 0.05, "Yes", "No"),
         `P-Value` = ifelse(p.value<0.001, "<0.001", paste("","",format(round(p.value,3), nsmall = 3), sep="&nbsp;" ))) %>%
  dplyr::select(-std.error, -p.value) %>%
  mutate(estimate = exp(as.numeric(estimate))) %>%
  rename("Variable" = term,
         "Coefficient" = estimate) %>% #Not sure about the name here
  relocate(Variable,'Coefficient',`Confidence (2.5%)`,`Confidence (97.5%)`,`P-Value`) %>%
  mutate(Variable = case_when(
    Variable == "(Intercept)" ~ "Intercept",
    Variable == "Sales_typeevening_sale" ~ "Evening Sale (vs. Day)",
    Variable == "dim2" ~ "Surface Area of Painting",
    Variable == "adj_century15th-16th c." ~ "15th-16th century (vs. 15th)",
    Variable == "adj_century16th c." ~ "16th century (vs. 15th)", #5
    Variable == "adj_century16th-17th c." ~ "16th-17th century (vs. 15th)",
    Variable == "adj_centuryn. m." ~ "Century not mentioned (vs. 15th)",
    Variable == "BY_SCHOOLBruges" ~ "Bruges School (vs. Antwerpen)",
    Variable == "BY_SCHOOLBruxelles" ~ "Bruxelles School (vs. Antwerpen)",
    Variable == "BY_SCHOOLFlemish" ~ "Flemish School (vs. Antwerpen)", #10
    Variable == "BY_SCHOOLGhent" ~ "Ghent School (vs. Antwerpen)",
    Variable == "BY_SCHOOLLeuven" ~ "Leuven School (vs. Antwerpen)",
    Variable == "BY_SCHOOLNetherlandish" ~ "Netherlandish School (vs. Antwerpen)",
    Variable == "PI_TOPICportrait" ~ "Portrait (vs. Religious topic)", #14
    Variable == "PI_TOPIClandscape" ~ "Landscape (vs. Religious topic)",
    Variable == "PI_TOPICallegory" ~ "Allegory (vs. Religious topic)",
    Variable == "PI_TOPICgenre scene" ~ "Genre Scene (vs. Religious topic)",
    Variable == "PI_TOPICmythology" ~ "Mythology (vs. Religious topic)",
    Variable == "PI_TOPICstill life" ~ "Still Life (vs. Religious topic)", #19
    Variable == "PI_TOPICothers" ~ "Other Topic (vs. Religious topic)",
    Variable == "CURRATS" ~ "Purchased in Schillings (vs. British Pound)",
    Variable == "CURRAUD" ~ "Purchased in Austrian Dollars (vs. British Pound)",
    Variable == "CURRBEF" ~ "Purchased in Belgian Francs (vs. British Pound)",
    Variable == "CURRCAD" ~ "Purchased in Canadian Dollars (vs. British Pound)", #24
    Variable == "CURRCHF" ~ "Purchased in Swiss Francs (vs. British Pound)",
    Variable == "CURRCZK" ~ "Purchased in Czech Koruna (vs. British Pound)",
    Variable == "CURRDEM" ~ "Purchased in Deutsche Mark (vs. British Pound)",
    Variable == "CURRDKK" ~ "Purchased in Danish Krone (vs. British Pound)",
    Variable == "CURRESP" ~ "Purchased in Spanish Peseta (vs. British Pound)", #29
    Variable == "CURREUR" ~ "Purchased in Euro (vs. British Pound)",
    Variable == "CURRFIM" ~ "Purchased in Finnish Markka (vs. British Pound)",
    Variable == "CURRFRF" ~ "Purchased in French Franc (vs. British Pound)",
    Variable == "CURRHUF" ~ "Purchased in Hungarian Forint (vs. British Pound)",
    Variable == "CURRIEP" ~ "Purchased in Irish Pound (vs. British Pound)", #34
    Variable == "CURRITL" ~ "Purchased in Italian Lira (vs. British Pound)",
    Variable == "CURRNLG" ~ "Purchased in Dutch Guilder (vs. British Pound)",
    Variable == "CURRNZD" ~ "Purchased in New Zealand Dollar (vs. British Pound)",
    Variable == "CURRPLN" ~ "Purchased in Polish Zloty (vs. British Pound)",
    Variable == "CURRSEK" ~ "Purchased in Swedish Krona (vs. British Pound)", 
    Variable == "CURRUSD" ~ "Purchased in US Dollars (vs. British Pound)",#39
    Variable == "CURRZAR" ~ "Purchased in S. African Rand (vs. British Pound)",
    Variable == "TYPE_COLLECTIONBelgium_coll" ~ "Belgium Collection (vs. Not Specified)",
    Variable == "TYPE_COLLECTIONmuseum_coll" ~ "Museum Collection (vs. Not Specified)", #42
    Variable == "TYPE_COLLECTIONnoble_coll" ~ "Noble Collection (vs. Not Specified)",
    Variable == "TYPE_COLLECTIONprivate_coll" ~ "Private Collection (vs. Not Specified)", #44
    Variable == "TYPE_COLLECTIONroyal_coll" ~ "Royal Collection (vs. Not Specified)",
    Variable == "t" ~ "Year Sold",
    Variable == "AH_TYPESBETA" ~ "2nd Tier Auction House (vs. Top Tier)", #47
    Variable == "AH_TYPESDELTA" ~ "3rd Tier Auction House (vs. Top Tier)",
    Variable == "AH_TYPESGAMMA" ~ "4th Tier Auction House (vs. Top Tier)",
    Variable == "Literature1" ~ "Publications on Painting (vs. None)", #50
    Variable == "DAT1" ~ "Date on Painting (vs. None)",
    Variable == "PI_TECHothers" ~ "Other Medium (vs. Oil)",
    Variable == "PI_TECHtempera" ~ "Tempera Medium (vs. Oil)", #53
    Variable == "PI_MATcanvas" ~ "Canvas Material (vs. Panel)", 
    Variable == "PI_MATcopper" ~ "Copper Material (vs. Panel)",
    Variable == "PI_MATothers" ~ "Other Material (vs. Panel)",
    Variable == "PI_CPI_OK" ~ "CPI at time of sale", #57
    Variable == "Prev_Attrib1" ~ "Had Previous Attribute (vs. Didn't)",
    Variable == "PI_TOPICportrait:t" ~ "Portrait * Year sold",
    Variable == "PI_TOPIClandscape:t" ~ "Landscape * Year sold", #60
    Variable == "PI_TOPICallegory:t" ~ "Allegory * Year sold",
    Variable == "PI_TOPICgenre scene:t" ~ "Genre Scene * Year sold",
    Variable == "PI_TOPICmythology:t" ~ "Mythology * Year sold",
    Variable == "PI_TOPICstill life:t" ~ "Still Life * Year sold",
    Variable == "PI_TOPICothers:t" ~ "Other Topic * Year sold",
    Variable == "EXHIB1" ~ "Been in an Exhibit (vs. not)", #66
    ))
```



```{r}
final_model_a[c(1:3, 6,10, 15,18, 29,36,38,40, 42,43, 44, 46, 47, 49,50, 51, 54, 55, 57,60), ]  %>%
  kable(format = "markdown", digits=3, caption ="Anonymous Model")
  
```
**The baseline for this model can be found in the appendix** We will consider the median hammer price in our interpretations rather than the mean as unconventionally high hammer prices caused by extreme bidding distort the average. Note that "accounting for all other factors" in the following interpretations refers to the baseline metrics. A 95% confidence interval was also calculated for each coefficient estimate.From the model, some interesting interpretations from the model are:

* As expected, the median hammer price for an evening sale vs. a day sale is expected to multiply by a factor of 5.534, after accounting for all other factors.
* For every additional 500 sqr cm (just over 0.5 sqr ft) the median hammer price is expected to multiply by a factor of 1.014, after accounting for all other factors.
* The median hammer price for a purchase in USD vs. Pounds is expected to multiply by a factor of 1.259, after accounting for all other factors.
* The median hammer price for a purchase from a private collected vs. an unspecified collection is expected to multiply by a factor of 1.485, after accounting for all other factors.
* The median hammer price for an auction not at top tier auction houses is expected to be less than at a top tier, after accounting for all other factors.
* The median hammer price for a painting with publications on the work is expected to multiply by a factor of 1.690 compared to no publications, after accounting for all other factors.
*The median hammer price for painting on canvas is expected to multiply by a factor of 0.742 compared to a panel after accounting for all other factors.
* For each additional year above 1946, the median hammer price for a sale is expected to multiply by a factor of 2.450, after accounting for all other factors.
* For each additional year above 1946, the median hammer price for a mythology vs. a religious topic painting is expected to multiply by a factor of 1.278	, after accounting for all other factors.

```{r}
#plot(full_model_anon)
```


```{r}
final_model_non_a = tidy(full_model_non_anon) %>% 
  dplyr::select(-statistic) %>%
  mutate(`Confidence (2.5%)` = exp(as.numeric(estimate) - ((1.96)*as.numeric(std.error))),
         `Confidence (97.5%)` = exp(estimate + ((1.96)*std.error)),
          Significant = ifelse(p.value < 0.05, "Yes", "No"),
         `P-Value` = ifelse(p.value<0.001, "<0.001", paste("","",format(round(p.value,3), nsmall = 3), sep="&nbsp;" ))) %>%
  dplyr::select(-std.error, -p.value) %>%
  mutate(estimate = exp(as.numeric(estimate))) %>%
  rename("Variable" = term,
         "Coefficient" = estimate) %>% #Not sure about the name here
  relocate(Variable,'Coefficient',`Confidence (2.5%)`,`Confidence (97.5%)`,`P-Value`) %>%
  mutate(Variable = case_when(
    Variable == "(Intercept)" ~ "Intercept",
    Variable == "Sales_typeevening_sale" ~ "Evening Sale (vs. Day)",
    Variable == "dim2" ~ "Surface Area of Painting",
    Variable == "adj_century15th-16th c." ~ "15th-16th century (vs. 15th)",
    Variable == "adj_century16th c." ~ "16th century (vs. 15th)",
    Variable == "adj_century16th-17th c." ~ "16th-17th century (vs. 15th)",
    Variable == "BY_SCHOOLBelgian" ~ "Beglian School (vs. Antwerpen)",
    Variable == "BY_SCHOOLBruges" ~ "Bruges School (vs. Antwerpen)",
    Variable == "BY_SCHOOLBruxelles" ~ "Bruxelles School (vs. Antwerpen)",
    Variable == "BY_SCHOOLFlemish" ~ "Flemish School (vs. Antwerpen)",
    Variable == "BY_SCHOOLGhent" ~ "Ghent School (vs. Antwerpen)",
    Variable == "BY_SCHOOLLeuven" ~ "Leuven School (vs. Antwerpen)",
    Variable == "BY_SCHOOLNetherlandish" ~ "Netherlandish School (vs. Antwerpen)",
    Variable == "PI_TOPICportrait" ~ "Portrait (vs. Religious topic)",
    Variable == "PI_TOPIClandscape" ~ "Landscape (vs. Religious topic)",
    Variable == "PI_TOPICallegory" ~ "Allegory (vs. Religious topic)",
    Variable == "PI_TOPICgenre scene" ~ "Genre Scene (vs. Religious topic)",
    Variable == "PI_TOPICmythology" ~ "Mythology (vs. Religious topic)",
    Variable == "PI_TOPICstill life" ~ "Still Life (vs. Religious topic)",
    Variable == "PI_TOPICothers" ~ "Other Topic (vs. Religious topic)",
    Variable == "CURRATS" ~ "Purchased in Schillings (vs. British Pound)",
    Variable == "CURRAUD" ~ "Purchased in Austrian Dollars (vs. British Pound)",
    Variable == "CURRBEF" ~ "Purchased in Belgian Francs (vs. British Pound)",
    Variable == "CURRCAD" ~ "Purchased in Canadian Dollars (vs. British Pound)",
    Variable == "CURRCHF" ~ "Purchased in Swiss Francs (vs. British Pound)",
    Variable == "CURRCZK" ~ "Purchased in Czech Koruna (vs. British Pound)",
    Variable == "CURRDEM" ~ "Purchased in Deutsche Mark (vs. British Pound)",
    Variable == "CURRDKK" ~ "Purchased in Danish Krone (vs. British Pound)",
    Variable == "CURRESP" ~ "Purchased in Spanish Peseta (vs. British Pound)",
    Variable == "CURREUR" ~ "Purchased in Euro (vs. British Pound)",
    Variable == "CURRFIM" ~ "Purchased in Finnish Markka (vs. British Pound)",
    Variable == "CURRFRF" ~ "Purchased in French Franc (vs. British Pound)",
    Variable == "CURRHUF" ~ "Purchased in Hungarian Forint (vs. British Pound)",
    Variable == "CURRIEP" ~ "Purchased in Irish Pound (vs. British Pound)",
    Variable == "CURRITL" ~ "Purchased in Italian Lira (vs. British Pound)",
    Variable == "CURRNLG" ~ "Purchased in Dutch Guilder (vs. British Pound)",
    Variable == "CURRNZD" ~ "Purchased in New Zealand Dollar (vs. British Pound)",
    Variable == "CURRPLN" ~ "Purchased in Polish Zloty (vs. British Pound)",
    Variable == "CURRSEK" ~ "Purchased in Swedish Krona (vs. British Pound)",
    Variable == "CURRUSD" ~ "Purchased in US Dollars (vs. British Pound)",
    Variable == "CURRZAR" ~ "Purchased in S. African Rand (vs. British Pound)",
    Variable == "TYPE_COLLECTIONBelgium_coll" ~ "Belgium Collection (vs. Not Specified)",
    Variable == "TYPE_COLLECTIONmuseum_coll" ~ "Museum Collection (vs. Not Specified)",
    Variable == "TYPE_COLLECTIONnoble_coll" ~ "Noble Collection (vs. Not Specified)",
    Variable == "TYPE_COLLECTIONprivate_coll" ~ "Private Collection (vs. Not Specified)",
    Variable == "TYPE_COLLECTIONroyal_coll" ~ "Royal Collection (vs. Not Specified)",
    Variable == "t" ~ "Year Sold",
    Variable == "AH_TYPESBETA" ~ "2nd Tier Auction House (vs. Top Tier)",
    Variable == "AH_TYPESDELTA" ~ "3rd Tier Auction House (vs. Top Tier)",
    Variable == "AH_TYPESGAMMA" ~ "4th Tier Auction House (vs. Top Tier)",
    Variable == "Literature1" ~ "Publications on Painting (vs. None)",
    Variable == "DAT1" ~ "Date on Painting (vs. None)",
    Variable == "PI_TECHothers" ~ "Other Medium (vs. Oil)",
    Variable == "PI_TECHtempera" ~ "Tempera Medium (vs. Oil)",
    Variable == "PI_MATcanvas" ~ "Canvas Material (vs. Panel)",
    Variable == "PI_MATcopper" ~ "Copper Material (vs. Panel)",
    Variable == "PI_MATothers" ~ "Other Material (vs. Panel)",
    Variable == "PI_CPI_OK" ~ "CPI at time of sale",
    Variable == "PI_ATTRIBattributed to" ~ "Atttributed to (vs. By)",
    Variable == "PI_ATTRIBcircle of" ~ "Circle of (vs. By)",
    Variable == "PI_ATTRIBfollower of" ~ "Follower of (vs. By)",
    Variable == "PI_ATTRIBmanner of" ~ "Manner of (vs. By)",
    Variable == "PI_ATTRIBschool of" ~ "School of (vs. By)",
    Variable == "PI_ATTRIBstyle of" ~ "Style of (vs. By)",
    Variable == "PI_ATTRIBstudio of" ~ "Studio of (vs. By)",
    Variable == "PI_ATTRIBafter" ~ "After (vs. By)",
    Variable == "Scientific_Investig1" ~ "Examined via Scientific Tech. (vs. Not)",
    Variable == "SIG1" ~ "Signed (vs. Not)",
    Variable == "PI_TOPICportrait:t" ~ "Portrait * Year sold",
    Variable == "PI_TOPIClandscape:t" ~ "Landscape * Year sold",
    Variable == "PI_TOPICallegory:t" ~ "Allegory * Year sold",
    Variable == "PI_TOPICgenre scene:t" ~ "Genre Scene * Year sold",
    Variable == "PI_TOPICmythology:t" ~ "Mythology * Year sold",
    Variable == "PI_TOPICstill life:t" ~ "Still Life * Year sold",
    Variable == "PI_TOPICothers:t" ~ "Other Topic * Year sold",
    Variable == "EXHIB1" ~ "Been in an Exhibit (vs. not)",
    Variable == "TYPE_REATTRIBnegative_reattrib" ~ "Reattrubted to a Less Profitable Attrib. (vs. not)",
    Variable == "TYPE_REATTRIBpositive_reattrib" ~ "Reattrubted to a More Profitable Attrib. (vs. not)",
    ))
```


```{r}
final_model_non_a[c(1:3, 6,10, 15,18, 30,40,43, 45, 47,48, 49,51,52, 54, 55, 60:70, 73),]  %>%
  kable(format = "markdown", digits=3, caption ="Non-Anonymous Model")
  
```

**The baseline for this model can be found in the Appendix.** Note that "accounting for all other factors" in the following interpretations refers to the baseline metrics. From the model, some interesting interpretations are:

* Similar to the anonymous work, the median hammer price for an evening sale vs. a day sale is expected to multiply by a factor of greater than 1, after accounting for all other factors.
* For every additional 500 sqr cm (just over 0.5 sqr ft) the median hammer price is expected to multiply by a factor of 1.014, after accounting for all other factors. This is the same factor as seen in the anonymous model.
* As expected, the median hammer price for attributions considered less prestigious as "by" are all expected to multiply by a factor of less than one, with "after" and "manner of" having the lowest estimates, after accounting for all other factors.
* The median hammer price for pieces that have been in an exhibit vs. have not is expected to multiply by a factor of 1.742, after accounting for all other factors.
* Similar to the anonymous work, the median hammer price for an dated painting vs. not dated is expected to multiply by a factor of greater than 1, after accounting for all other factors.
* Similar to the anonymous work, the median hammer price for an painting on canvas vs. on a panel is expected to multiply by a factor of less than 1, after accounting for all other factors.
* For each additional year above 1946, the median hammer price for a sale is expected to multiply by a factor of 1.074, after accounting for all other factors. Like the anonymous model, this factor is greater than one.
* For each additional year above 1946, the median hammer price for a landscape vs. a religious topic painting is expected to multiply by a factor of 0.988, after accounting for all other factors. Unlike the anonymous model, this factor is less than one although the coefficient was not deemed significant in the anonymous model.

# Discussion

Some limitations to this analysis rest in the asymmetry of accessible data for anonymous vs. non-anonymous work. There was substantially more data for non-anonymous pieces potentially due to the fact that auctions, in general, prioritize the sales of attributed work over anonymous work, or potentially due to the fact that there are less anonymous Flemish paintings from the 15th - 17th c. in existence. Another limitation is that there is no evidence to believe that findings for these paintings (Flemish 15th - 17th century) can be extrapolated to other genres. The findings of this analysis are informative and enlightening, yet there is no evidence to suggest they are generalizable to other genres of work.  

As seen in the interpreted results, the two fitted model for anonymous and non-anonymous works had both similar and dissimilar associations between median hammer price and independent variables after adjusting for baseline metrics. The purpose of creating two models was to be able to isolate factors associated with median hammer price that were not associated with the subjective reputation or clout of a painting's creator. Even still, both the anonymous and non-anonymous model (at the baseline of highest attribution "by") presented evidence for some similar associations between the response (median hammer price) and purely objective independent variables such as type of auction (evening or day), painting surface area, whether the painting was dated, material of the painting, and year of the sale. From the non-anonymous model, there is evidence to suggest that the attribution title is significantly associated with the median hammer price. These findings help art historians and auctioneers to contextualize how art is valued in contemporary markets and how, if stripped away of material prestige, there are inherent qualities of art tied to its worth.Analyzing anonymous art sales serves as a way to distill artwork (in this case Flemish paintings from the 15th-17th century) down to the pure qualities that are associated with it's value. 

Ultimately, with a significant lack of accessibility and transparency in auction houses and art markets, there remains an extensive amount of meaningful research to be done, especially in the area of anonynmous work. Hopefully, analyses like this can be conducted on other areas of art and motivate art market players--who have a notorious reputation for elusive pricing and unobtainable records/data--to engage in more transparent transactions and art valuations.


# Appendix

```{r, fig.height= 3}
#1A
grid.arrange(Subject_Plot2, Subject_Plot, ncol= 2, top = "Figure 1A: Comparison of Painting Subject
Between Non-Anonymous and Anonymous Paintings")

```

```{r fig.height= 4}
#2A
grid.arrange( SubjectPrice_Plot_Condensed1, SubjectPrice_Plot_Condensed , top= "Figure 2A: Hammer Price Medians by Subject", ncol=1)
```

```{r fig.height= 2.5}
#3A
ggplot(data, aes(x=DATE, y= log(HAM_USD)))+geom_point() +labs(title = "Figure 3A: Log(Hammer Price in 2015 USD) vs. Date of Sale", x= "Date", y="Log(Hammer Price USD)")

```

```{r}
#4A
grid.arrange(collection_non_anon, collection_anon,n_anon_sal, anon_sal,  ncol=2, top = "Figure 4A: Consistent Trends Seen in Sale Type and Collection Type")
```

## Releveling/Baseline Assumptions For Both Models
* Antwerpen School was made the baseline for the school of a painting because it has the most observations.

* 15th century was made the baseline for painting's century because it is the earliest time period and it is most logical to interpret coefficients in chronological order.

* The Religious Topic was made the baseline for painting subject matter because it has the most observations.

* Great Britain's Pound was made the baseline for currency used in sale because has the most observations.

* The un-mentioned collection type was made the baseline for collection type as it has the most observations and it has the lowest distribution in price.

* The most top tier auction house was made the baseline for auction house prestige as it has the most observations and is logical to compare from top organizations

* Oil medium was made the baseline for painting medium as it has the most observations and, during the 15-17th century, most work was done in oil.

* Panel was made the baseline for material as it has the most observations.


## Removed Variables

## Baseline for Anonymous Model 
An evening sale; The dataset's average painting surface area of 4,956 sqr cm; 15th century painting; Antwerpen School; Paid for with British Pounds; Collection type not specified; Sold in the first year recorded in the dataset (1946); Of a religious topic; Sold at a top tier auction house; No publications on the painting; No date on the painting; Painted in oil on a panel; CPI at time of sale was 8.3 (recorded for 1946); Was not Reattributed; And has not been in an exhibit.

## Baseline for Non-Anonymous Model 
An evening sale; The dataset's average painting surface area of 4956 sqr cm; 15th century painting; Antwerpen School; Paid for with British Pounds; Collection type not specified; Sold in the first year recorded in the dataset (1946); Of a religious topic; Sold at a top tier auction house; No publications on the painting; No date on the painting; Painted in oil on a panel; CPI at time of sale was 8.3 (recorded for 1946); Was not Reattributed; Has not been in an exhibit; Was not examined via scientific technology; Was not signed.
